\section{Video game development as software development} \label{game-development-sw}
\paragraph{Successful software}
Game development is a branch of software development, however, many argue that it is a separate genre
due to its completely different working pipelines and different composition of development teams, let alone the challenges 
related to project funding. A nicely written code, good functionality and user experience, fulfilling business specifications 
and remaininig within budget are usually enough for any commercial software to be successful on the market. In case of game 
development there are other factors that could potentially undermine the process leading to commercial failures.
\paragraph{Successful video game}
In fact, the end product of game development is mostly an entertainment or educational software. Apart from the code 
base that is basically the essence of any software product, the success of video games requires artistic assets, 
gameplay elements and also an immersive storyline or world creation fitting seamlessly together.
These components bring game development closer to creative industries like filmmaking. Actually, it is quite easy to mess
up any of the previously described elements or the interactions between them. 
A video game aiming to be a top-tier product cannot have good controls but horrible graphics
or beautiful graphics but nasty gameplay dynamics. Additionally, a good story helps to retain users so that
they do not turn away from the game too soon. On the other hand, there are many games considered as successful without
nice graphics or story, simply because they are "fun" to play. There is no formal way to define "fun", hence it becomes
a difficult task to define the ultimate definition of "good" or "succesful" video games, just like in case of movies.
\paragraph{Team composition}
...
\paragraph{Version control in game development}
The previously mentioned characteristics of video game production affect also the version controlling activities applied
during development. Different teams have different needs and a good VCS can make their interactions smoother by adding
as least additional administrative burden as possible while speeding up development cycles.

\paragraph{}
After the more theoretical first two sections of the paper, the next sections guide through a simple game development
project using the most widespread version control system of the industry, 
Helix Core\textsuperscript{\texttrademark}.